Tracing the Stellar Halos of Massive Galaxies to 100 kpc at $0.3<z<0.5$ using Hyper Suprime-Cam

### 2017-06-07 draft/paper1_v11.tex
Jenny's comment: 7; and more references

	The ellipticity of the isophote contains information about the 3-D geometry 
	(e.g. \citealt{Chang2013, Mitsuda2017}) and kinematics (e.g. 
	\citealt{Cappellari2012, Weijmans2014}) of stars in massive galaxies.  
	The left panel of Fig \ref{fig:ell_color} shows the ellipticity profiles of HSC 
	massive galaxies and highlights the median profiles for the same three \mtot{} 
	bins used in Fig \ref{fig:avg_prof}. 
    We also compare our ellipticity profiles with previous ones that are based on 
	image stacking techniques (the PSF-removed $i$-band from \citealt{Tal2011}, 
	the concentration galaxies with $11.0<$\logms{}$<11.4$ from \citealt{DSouza2015}).
	As expected, the ellipticity profile from image stacking method tends to be 
	shallower than the HSC one.  
	Uncertainties in aligning galaxies before stacking and the intrinsic isophotal 
	twist can lead to this effect.

	In general, the ellipticity of massive galaxy slowly increases with radius.
	One can even notice this trend by directly comparing the shape of galaxy between 
	SDSS and HSC images (e.g. Fig \ref{fig:sdss_compare}).  
	More interestingly, the ellipticity profiles clear depend on \mtot{}: 
	at ${\sim} 10$ kpc, median ellipticities from all three bins are low and similar 
	($< 0.2$); but more massive galaxies become increasingly more elongated in their
	stellar halo. 	
	For the \logms{}$>11.8$ galaxy, its median ellipticity profile becomes steeper 
	at $>10$ kpc, and the ellipticity steadily increases from $e\le 0.2$ to 
	$e{\sim} 0.4$ at 50-60 kpc.
	This is consistent with studies of nearby massive galaxies, both from 1-D 
	ellipticity profiles and 2-D modeling results \citep{Gonzalez2005, 
	Huang2013a, Spavone2017}.
	Although this phenomenon was well-documented, clear evidence of mass-dependent
	ellipticity profiles and the potentially anti-correlated slopes of \mden{} and 
	ellipticity profiles has not been identified.
	If accreted stars dominate the stellar halos of massive galaxies, this 
	mass-dependent ellipticity profile may lead us to some insights about the 
	differences in their assembly history (e.g. average time since last merger, 
	average merger mass ratio).
	Previous simulations often focused on reproducing the rounder average shape 
	and slow-rotating nature of massive ETGs (e.g. \citealt{Wu2014}), so the 
	projected ellipticity profiles and their correlations with the kinematic of 
	stars and merging history have not been well explored.

@@

    %The mass-dependent nature we find in the \mden{} and ellipticity profiles of 
    %massive galaxies are consistent with the two-phase formation scenario. 
    We find that the outer halos of massive elliptical galaxies grow more prominent and 
    more elliptical with increasing stellar mass.
    According to the two-phase formation scenario, the inner 5--10 kpc of these 
    massive central galaxies are formed at $z>1$ during an intense period of 
    \textit{in situ} star formation. 
    The outskirts of massive galaxies are then built up through a more gradual second 
    phase of evolution (the \textit{ex situ} phase) that is dominated by mass assembly via 
    accretion and merger.
    Non-dissipative mergers, especially the minor ones, mostly deposit stars in the 
    outskirts of the centrals and do not have a large impact on the central \mden{} 
    profile (e.g. \citealt{Oogi2013, Bedorf2013}). \jenny{Mike BK \& Ma paper too.}
    Given the stochastic nature of the merging process, it is easy to understand why 
    the \mden{} profiles of massive galaxies are similar in the inner region but show
    large and continuous scatter in the outskirt.

@@

    Also under this picture, the shape of the stellar halo should preserve information
    about the merging history and even the dark matter halos. 
    Simulations show that, slowly-rotating massive ETGs that experienced multiple 
    minor-mergers, the shape of the stellar and dark matter halos are closely 
    correlated (e.g. \citealt{Wu2014}). 
    However, simulation like the one in \citet{Wu2014} predicts that more massive 
    galaxies should be rounder in the outskirt.
    This difference deserves more investigations using stellar kinematics and 
    simulations. 
    It may reflect the importance of major merger in shaping the most massive 
    galaxies. 
    Major merger with central galaxy of massive halo often happens on near-radial 
    orbits (e.g. \citealt{Murante2007}), hence leading to radially biassed stellar 
    orbits and more elongated halo. \jenny{Semyeongs paper may have some interesting relevant 
    citations about cluster-scale simulations, that also show ICL to grow more elliptical at 
    large radius.}

>>>>

	The ellipticity of the isophote contains information about the 3-D geometry 
	(e.g. \citealt{Tremblay1995, Tremblay1996, Chang2013, RodriguezPadilla2013, 
	Mitsuda2017}) and kinematics (e.g. \citealt{Cappellari2012, Weijmans2014}) of 
	stars in massive galaxies.  
	The left panel of Fig \ref{fig:ell_color} shows the ellipticity profiles of HSC 
	massive galaxies and highlights the median profiles for the same three \mtot{} 
	bins used in Fig \ref{fig:avg_prof}. 
    We also compare our ellipticity profiles with previous ones that are based on 
	image stacking techniques (the PSF-removed $i$-band from \citealt{Tal2011}, 
	the concentration galaxies with $11.0<$\logms{}$<11.4$ from \citealt{DSouza2015}).
	As expected, the ellipticity profile from image stacking method tends to be 
	shallower than the HSC one.  
	Uncertainties in aligning galaxies before stacking and the intrinsic isophotal 
	twist can lead to this effect.

	In general, the ellipticity of massive galaxy slowly increases with radius.
	One can even notice this trend by directly comparing the shape of galaxy between 
	SDSS and HSC images (e.g. Fig \ref{fig:sdss_compare}).  
	More interestingly, the ellipticity profiles clear depend on \mtot{}: 
	at ${\sim} 10$ kpc, median ellipticities from all three bins are low and similar 
	($< 0.2$); but more massive galaxies become increasingly more elongated in their
	stellar halo. 	
	For the \logms{}$>11.8$ galaxy, its median ellipticity profile becomes steeper 
	at $>10$ kpc, and the ellipticity steadily increases from $e\le 0.2$ to 
	$e{\sim} 0.4$ at 50-60 kpc.
	This is consistent with studies of nearby massive galaxies, both from 1-D 
	ellipticity profiles and 2-D modeling results \citep{Porter1991, Gonzalez2005, 
	Zibetti2005, Spavone2017; Huang2013a, Oh2017}.
	Although this phenomenon was well-documented, clear evidence of mass-dependent
	ellipticity profiles and the potentially anti-correlated slopes of \mden{} and 
	ellipticity profiles has not been identified.
	If accreted stars dominate the stellar halos of massive galaxies, this 
	mass-dependent ellipticity profile may lead us to some insights about the 
	differences in their assembly history (e.g. average time since last merger, 
	average merger mass ratio).
	Previous simulations often focused on reproducing the rounder average shape 
	and slow-rotating nature of massive ETGs (e.g. \citealt{Wu2014}), so the 
	projected ellipticity profiles and their correlations with the kinematic of 
	stars and merging history have not been well explored.

@@

    %The mass-dependent nature we find in the \mden{} and ellipticity profiles of 
    %massive galaxies are consistent with the two-phase formation scenario. 
    We find that the outer halos of massive elliptical galaxies grow more prominent and 
    more elliptical with increasing stellar mass.
    According to the two-phase formation scenario, the inner 5--10 kpc of these 
    massive central galaxies are formed at $z>1$ during an intense period of 
    \textit{in situ} star formation. 
    The outskirts of massive galaxies are then built up through a more gradual second 
    phase of evolution (the \textit{ex situ} phase) that is dominated by mass assembly via 
    accretion and merger.
    Non-dissipative mergers, especially the minor ones, mostly deposit stars in the 
    outskirts of the centrals and do not have a large impact on the central \mden{} 
    profile (e.g. \citealt{BoylanKolchin2008, Oogi2013, Bedorf2013}).
    Given the stochastic nature of the merging process, it is easy to understand why 
    the \mden{} profiles of massive galaxies are similar in the inner region but show
    larger scatter in the outskirt.

@@

    Also under this picture, the shape of the stellar halo should preserve information
    about the merging history and even the dark matter halos. 
    Simulations show that, slowly-rotating massive ETGs that experienced multiple 
    minor-mergers, the shape of the stellar and dark matter halos are closely 
    correlated (e.g. \citealt{Wu2014}). 
    The more elongated outer halo and the trend between ellipticity profile and 
    stellar mass may reflect that the orbital properties of infalling satellite are 
    not random. 
    In simulations, satellite orbit becomes more radial when it falls into more 
    massive halos and when the satellite-central mass ratio is high (e.g. 
    \citealt{Murante2007, Wetzel2011, Jiang2015}.
    In principle, these results help explain the observed trend, and emphasize the 
    importance of major merger in shaping the halo of massive galaxies. 
    However, simulation like the one in \citet{Wu2014} predicts that more massive 
    galaxies should be rounder in the outskirt.
    This difference deserves more investigations using stellar kinematics and 
    simulations.
